### 2021-05-21 README.Rmd
Last edits

> Pollard, Dominic (2020). _`r Title`_. Name of journal/book, <https://doi.org/xxx/xxx>

@@

> Pollard, Dominic (2020). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

Or you can install this compendium as an R package from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("DCPollard94/knossoscemeteries")
```
### Licenses

>>>>

> Pollard, Dominic (2021). _`r Title`_. Name of journal/book, <https://doi.org/xxx/xxx>

@@

> Pollard, Dominic (2021). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

Or you can install this compendium as an R package from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("DCPollard94/knossoscemeteries")
```

The compendium is also available from figshare at: https://doi.org/10.6084/m9.figshare.13019588.v1

### Licenses
